\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-11 paper.tex

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n, p, k, m$ & number of observations, variables, embedding dimension, number of non-empty bins, respectively\\
$\mathbfit{X}, \mathbfit{x}$ & $p$-dimensional data (population, sample)\\
$\mathbfit{y}$ & $k$-dimensional layout\\
$P$ & orthonormal basis, generating a $d\text{-}dimensional$ linear projection of $p$-dimensional data\\
$T$ & true  model\\
\addlinespace
$g$ & functional mapping from \pD{} to \kD{}, especially as prescribed by NLDR\\
$\mathbfit{\theta}$ & (Hyper-) parameters for NLDR method\\
$y_\text{max}$ & maximum value of the scaled second embedding component\\
$r$ & ranges of the embedding components\\
$b$ & bins\\
\addlinespace
$a_r$ & aspect ratio of the 2D layout before scaling\\
$s$ & hexagonal size (radius of the outer circle surrounding the hexagon)\\
$(x_s, \ y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$, $q_y$ & buffer amount along the x and y axes\\
$h_s$, $v_s$ & horizontal and vertical distance between adjacent hexagon bin centroids\\
\addlinespace
$d_x$, $d_y$ & horizontal spacing and adjusted vertical spacing for hexagonal coordinates\\
$b_x$, $b_y$ & number of hexagon bins along the x and y axes\\
$b$, $b'$ & total and non-empty hexagon bins in the grid\\
$n_k$ & number of observations within the $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of the $k^{th}$ hexagon\\
\addlinespace
$C^{(j)}$ & $j$-dimensional bin centers\\
\bottomrule
\end{tabular}
\endgroup{}

>>>>

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n, p, k, m$ & number of observations, variables, embedding dimension, number of non-empty bins, respectively\\
$\mathbfit{X}, \mathbfit{x}$ & $p$-dimensional data (population, sample)\\
$\mathbfit{y}$ & $k$-dimensional layout\\
$P$ & orthonormal basis, generating a $d\text{-}dimensional$ linear projection of $p$-dimensional data\\
$T$ & true  model\\
\addlinespace
$g$ & functional mapping from \pD{} to \kD{}, especially as prescribed by NLDR\\
$\mathbfit{\theta}$ & (Hyper-) parameters for NLDR method\\
$y_\text{max}$ & maximum value of the scaled second embedding component\\
$r$ & ranges of the embedding components\\
$b$ & bins\\
\addlinespace
$a_r$ & aspect ratio of the 2D layout before scaling\\
$s$ & hexagonal size (defined as the radius of the outer circle surrounding the hexagon)\\
$(x_s, \ y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$, $q_y$ & buffer amount along the x and y axes\\
$h_s$, $v_s$ & horizontal and vertical distance between adjacent hexagon bin centroids\\
\addlinespace
$d_x$, $d_y$ & horizontal spacing and adjusted vertical spacing for hexagonal coordinates\\
$b_x$, $b_y$ & number of hexagon bins along the x and y axes\\
$b$, $b'$ & total and non-empty hexagon bins in the grid\\
$n_k$ & number of observations within the $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of the $k^{th}$ hexagon\\
\addlinespace
$C^{(j)}$ & $j$-dimensional bin centers\\
\bottomrule
\end{tabular}
\endgroup{}
